\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{times} % Optional: Use Times font
\usepackage{parskip} % Adds space between paragraphs instead of indent
\usepackage{hyperref} % Needed for hyperlinked email/URLs

\setlength{\parindent}{0pt} % No paragraph indentation

\begin{document}

% --- Your Contact Information --- 
\begin{flushleft}
\textbf{James Smith} \\
+61 (437) 273 729 \\
\href{mailto:james@digijin.com}{james@digijin.com} \\
\href{https://www.linkedin.com/in/digijin/}{linkedin.com/in/digijin} \\
\href{https://github.com/digijin}{github.com/digijin}
\end{flushleft}

\vspace{1em}

% --- Date ---
\today

\vspace{2em} % Increased space as recipient block is removed

% --- Salutation ---
Dear Hiring Manager or Hiring Team,

\vspace{1em}

% --- Body Paragraph 1: Introduction --- 
I am writing to express my strong interest in relevant Engineering Manager or Senior/Lead Software Engineer positions where I can leverage my extensive experience. With over 20 years in web development, including significant expertise in technical leadership, project management, and full-stack engineering for prominent Australian brands, I am confident I possess the skills and experience necessary to make a significant contribution to your organization.

\vspace{1em}

% --- Body Paragraph 2: Alignment with Role/Company --- 
Throughout my career at companies such as ubank, Fox Sports/Foxtel, and Nine/nineMSN, I have successfully led teams, architected scalable solutions, and driven process improvements. My background includes managing large-scale data migrations, optimizing development workflows, and providing technical direction on critical projects. My expertise spans Node.js, TypeScript, cloud infrastructure (AWS), CI/CD, Agile methodologies, and team leadership, aligning well with the requirements of challenging engineering and management roles.

\vspace{1em}

% --- Body Paragraph 3: Key Achievements Summary --- 
My experience encompasses leading complex initiatives, such as the \$12B ubank customer migration, significantly improving delivery times for projects like the Fox Sports Ditto Match Centres, rebuilding high-traffic homepages like nine.com.au, and enhancing overall system performance and scalability through targeted technical improvements.

\vspace{1em}

% --- Conclusion --- 
Thank you for considering my profile. I have attached my resume for your detailed review and welcome the opportunity to discuss how my qualifications and experience can benefit your team. I am excited about the possibility of contributing to challenging and rewarding projects.

\vspace{1em}

% --- Closing --- 
Sincerely, \\
\vspace{2em} % Space for signature if printed
James Smith

\end{document} 