\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{titlesec, enumitem, hyperref}
\usepackage{xcolor}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\renewcommand{\labelitemi}{$\bullet$}

\begin{document}

\begin{center}
    {\Huge \textbf{James Smith}} \\
    \href{https://www.linkedin.com/in/digijin/}{LinkedIn} | \href{https://github.com/digijin}{GitHub} \\
    \href{mailto:james@digijin.com}{james@digijin.com} | +61 (437) 273 729
\end{center}

\section*{Summary}
Experienced Engineering Manager with a strong background in web development and team leadership. Proven track record of delivering high-quality projects on time and within budget. Skilled in JavaScript, Node.js, and cloud technologies.

\section*{Skills}
\begin{itemize}
    \item Programming Languages: JavaScript, TypeScript, CSS
    \item Frameworks: Node.js, Angular, React, Express
    \item Tools: Git, AWS, Atlassian Suite, WordPress, Sitecore
    \item Soft Skills: Team Leadership, Project Management, Mentoring, Recruitment
    \item Other: Agile, Scrum, Kanban, Lean, Continuous Integration, Continuous Deployment
\end{itemize}

\section*{Work Experience}

\textbf{86400 / ubank} \hfill \textit{March 2022 - Present} \\
Engineering Manager \\
\textit{Technologies: TypeScript, Node, Angular, Mobile}
\begin{itemize}
    \item Led the migration of ubank customers to the 86400 infrastructure, managing the transfer of over \$12 billion in customer funds.
    \item Developed personal finance tools for tracking income, bills, spending, and budgeting.
    \item Applied expertise in fraud detection and transactional processes.
\end{itemize}

After joining the company subsequent to ubank's acquisition of 86400, I was made responsible for overseeing the 
seamless migration of the ubank customer base onto the 86400 infrastructure. This process entailed the establishment
of new bank accounts for a substantial customer cohort, encompassing hundreds of thousands of individuals, and the 
successful transfer of over \$12 billion in customer funds to their respective new accounts, ensuring uninterrupted 
access to their finances.

Following the migration, my team transitioned into a dynamic feature team, actively contributing to the advancement 
of ubank's product roadmap. We designed and developed personal finance tools to track income, bills and spending as 
well as tools to budget and allocate money for our customers. Additionally, I have leveraged my expertise in fraud 
detection and transactional processes to support various projects, further enhancing organizational objectives.

\textbf{Fox Sports / Foxtel} \hfill \textit{August 2017 - February 2022} \\
Web Development Manager \\
\textit{Technologies: JavaScript, CSS, Node.js, AWS, Atlassian Suite, WordPress}
\begin{itemize}
    \item Managed a team of 6-12 developers working on the Fox Sports website.
    \item Improved development processes, reducing project delivery time from 3 months to 4 weeks.
    \item Led multiple teams at Foxtel, contributing to automated TV and movie pages, rebuilding the design system, and updating the "My Account" sections.
\end{itemize}

\textbf{Mi9 / nineMSN / Nine} \hfill \textit{June 2014 - August 2017} \\
Technical Development Manager \\
\textit{Technologies: JavaScript, CSS, Node.js, Sitecore, AWS, Git}
\begin{itemize}
    \item Led a team developing core properties for the ninemsn suite.
    \item Initiated and architected a Node.js rebuild of "Network Home," supporting 3M users and generating significant ad revenue.
    \item Won the internal "Connected Leader" award for technical leadership.
\end{itemize}

\textbf{Mi9} \hfill \textit{January 2014 - June 2014} \\
Lead Developer – Studios team \\
\textit{Technologies: JavaScript, CSS, Node.js, Git, Agile}
\begin{itemize}
    \item Managed a team of 4 frontend developers while actively contributing to development.
    \item Mentored team members and established personal development plans.
    \item Led recruitment and improved development processes.
\end{itemize}

\textbf{Rockwell Information Services} \hfill \textit{June 2011 - July 2013} \\
Lead Developer \\
\textit{Technologies: PHP5, Zend Framework, MySQL, LAMP, Git, Salesforce Integration}
\begin{itemize}
    \item Led a team of PHP developers in building a multilingual LMS (Learning Management System).
    \item Integrated Salesforce for managing certifications and discount schemes worth millions.
    \item Maintained an existing LMS used worldwide for training and certification.
\end{itemize}

\textbf{Freelance and Consulting} \hfill \textit{2004 - Present} \\
\textit{Various small projects in web development and game development.}

\section*{Education}

\textbf{TAFE Crows Nest} \hfill \textit{2004} \\
Diploma in Digital Media \\
\textbf{TAFE Crows Nest} \hfill \textit{2003} \\
Certificate IV in Digital Media (Merit Award)

\end{document}